Making (Secure) FETCH Happen: \\ \vspace{2 mm} {\large End-to-End Metadata Security for IMAP}

### 2015-04-29 paper/paper.tex
figure illustrating whole system

@@

The first is unacceptable, given the target user group described in Section~\ref{targetuser}, as this would violate user expectations. Users expect to be able to access their content across all of their devices, and keeping all messages on the local machine only would thereby force them to adjust their usage patterns. To implement the second possibility, we would need to describe a server infrastructure for storing messages and synchronizing across multiple possible clients who have subscribed to updates on messages stored in the system -- which is to say, (a subset of) the functions that the IMAP server is designed to perform. This brings us to our final option: using a modified version of existing IMAP technology, as we have described.

@@

  \begin{tikzpicture}[node distance=2.5cm]
  \node (alice) [box] {Alice};
  \node (smtpa) [box, above of=alice] {Alice's metadata-\\ secure server};
  \node (cloud) [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em, right of=smtpa, xshift=1.3cm] {Network};
  \node (imapb) [box, right of=cloud, xshift=1.3cm] {Bob's metadata-\\secure server};

@@

  \end{tikzpicture}

@@

  \begin{tikzpicture}[node distance=2.5cm]
  \node (alice) [box] {Alice};
  \node (smtpa) [box, above of=alice] {Alice's legacy \\ SMTP server};
  \node (cloud) [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em, right of=smtpa, xshift=1.3cm] {Network};
  \node (imapb) [box, minimum width = 4cm, right of=cloud, xshift=1.4cm] {Bob's legacy \\ IMAP server \\
      \trimbox{0cm 0cm 0cm -.2cm}{
          \begin{tikzpicture}
              \node (index) [box, minimum height=.5cm, outer sep=.2] {INDEX};
          \end{tikzpicture}
      } 
    };

@@

\subsection{Command Translations}
In the IMAP server/client model, the client sends commands to the server, and the server responds based on its state and contents. These commands are the primary form of synchronizing data between the server and its clients. The \project module sits between the client and the legacy IMAP module. It translates arguments, processes data, and returns results that give the client a pseudo-view of the contents of the IMAP server informed by the contents of the metadata INDEX.

We can classify mailboxes by two features: their visibility to the server, and their visibility to the client. When the client's view of the mailbox is used, it is referred to as a pseudo-mailbox. There are four possible mailbox classifications, as illustrated in the table below. The classification determines the actions that the module takes in response to each command. A PSEUDO mailbox is not mirrored in the IMAP server; it exists only in the INDEX and is thus only known to clients following the \project protocol. SMTorP is an example of a PSEUDO mailbox. A HYBRID mailbox exists both in the IMAP server and in the INDEX. This is a mailbox such as INBOX, which must also be known to the IMAP server as a location for the delivery of incoming messages. A PSEUDO/HIDDEN pseudo-mailbox neither exists in the IMAP server nor is known to the client. It is only for the internal use of the \project module. The FAKE\_MESSAGES pseudo-mailbox used by the scheduler is an example of this type of pseudo-mailbox. An ACTUAL/HIDDEN mailbox is known to the IMAP server but not to the \project client. The CRYPTOBLOBS mailbox, the mailbox in which all encrypted messages are stored on the IMAP server, is an example of this type of mailbox. These classifications are shown in this table.

\begin{tabular}{ rr|c|c| }

@@

&\multicolumn{1}{r}{}
 &  \multicolumn{1}{c}{Yes}
 & \multicolumn{1}{c}{No} \\
\cline{3-4}
\multirow{2}{*}{Visible to Server?} & Yes & INBOX & CRYPTOBLOBS \\
\cline{3-4}
& No & SMTorP & FAKE\_MESSAGES \\
\cline{3-4}
\end{tabular}

@@

  \begin{tikzpicture}[node distance=8cm]
  \node (\project) [box, minimum height=2cm] {\project};

>>>>

\usetikzlibrary{matrix,shapes.multipart,shapes.geometric,fit,scopes}
\tikzset{
  >= latex,
  el/.style={ellipse, draw, text width=8em, align=center},
  rs/.style={rectangle split, draw, rectangle split parts=#1},
  ou/.style={draw, inner xsep=1em, inner ysep=1ex, fit=#1}
}

@@

The first is unacceptable, given the target user group described in Section~\ref{targetuser}, as this would violate user expectations. Users expect to be able to access their content across all of their devices, and keeping all messages on the local machine only would thereby force them to adjust their usage patterns. To implement the second possibility, we would need to describe a server infrastructure for storing messages and synchronizing across multiple possible clients who have subscribed to updates on messages stored in the system -- which is to say, (a subset of) the functions that the IMAP server is designed to perform. This brings us to our final option: using a modified version of existing IMAP technology, as illustrated in the figure below.

\begin{center}

\includegraphics[width=0.6\textwidth]{server_client_boxes}

\end{center}

@@

\medskip

\begin{center}
  \begin{tikzpicture}[node distance=2.5cm]
  \node (alice) [box] {Alice};
  \node (smtpa) [box, above of=alice] {Alice's metadata-\\ secure server};
  \node (cloud) [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em, right of=smtpa, xshift=1.3cm] {Network};
  \node (imapb) [box, right of=cloud, xshift=1.3cm] {Bob's metadata-\\secure server};

@@

  \end{tikzpicture}
\end{center}

@@

\medskip

\begin{center}
  \begin{tikzpicture}[node distance=2.5cm]
  \node (alice) [box] {Alice};
  \node (smtpa) [box, above of=alice] {Alice's legacy \\ SMTP server};
  \node (cloud) [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em, right of=smtpa, xshift=1.3cm] {Network};
  \node (imapb) [box, minimum width = 4cm, right of=cloud, xshift=1.4cm] {Bob's legacy \\ IMAP server \\
      \trimbox{0cm 0cm 0cm -.2cm}{
          \begin{tikzpicture}
              \node (index) [box, minimum height=.5cm, outer sep=.2] {INDEX};
          \end{tikzpicture}
      } 
    };

@@

\subsection{Command Translations}
In the IMAP server/client model, the client sends commands to the server, and the server responds based on its state and contents. These commands are the primary form of synchronizing data between the server and its clients. The \project module sits between the client and the legacy IMAP module. It translates arguments, processes data, and returns results that give the client a pseudo-view of the contents of the IMAP server informed by the contents of the INDEX metadata store.

We can classify mailboxes by two features: their visibility to the IMAP server, and their visibility to the client of the \project module (``the client''). All mailboxes are visible internally to \projectnospace. ``Mailbox'' is a general term referring to any combination of visibility options. When referring to \projectnospace's internal representation of a mailbox, we will specifically refer to it as a pseudo-mailbox (using lowercase type). For example, a message can appear to the client to be in the pseudo-mailbox INBOX, while the server is in reality storing that particular message in its CRYPTOBLOBS mailbox. The following table gives examples of particular mailboxes for each of the possible combinations of client-server visibilities, followed by further explanation of its contents.

\begin{center}
\begin{tabular}{ rr|c|c| }

@@

&\multicolumn{1}{r}{}
 &  \multicolumn{1}{c}{Yes}
 & \multicolumn{1}{c}{No} \\
\cline{3-4}
\multirow{2}{*}{Visible to Server?} & Yes & INBOX & CRYPTOBLOBS \\
\cline{3-4}
& No & SMTorP & FAKE\_MESSAGES \\
\cline{3-4}
\end{tabular}
\end{center}

\medskip

As the table shows, there are four possible mailbox classifications. The classification determines the actions that the module takes in response to each command. We name each of these, for ease of future identification:

\begin{itemize}

\item \textbf{PSEUDO}: A PSEUDO mailbox is not mirrored in the IMAP server; it exists only in the INDEX and is thus only known to clients following the \project protocol. SMTorP is an example of a PSEUDO mailbox.
\item \textbf{HYBRID}: A HYBRID mailbox exists both in the IMAP server and in the INDEX. This is a mailbox such as INBOX, which must also be known to the IMAP server as a location for the delivery of incoming messages.
\item \textbf{PSEUDO/HIDDEN}: A PSEUDO/HIDDEN pseudo-mailbox neither exists in the IMAP server nor is known to the client. It is only for the internal use of the \project module. The FAKE\_MESSAGES pseudo-mailbox used by the scheduler is an example of this type of pseudo-mailbox.
\item \textbf{ACTUAL/HIDDEN}: An ACTUAL/HIDDEN mailbox is known to the IMAP server but not to the \project client. The CRYPTOBLOBS mailbox, the mailbox in which all encrypted messages are stored on the IMAP server, is an example of this type of mailbox.

\end{itemize}

@@

\medskip

\begin{center}
  \begin{tikzpicture}[node distance=8cm]
  \node (\project) [box, minimum height=2cm] {\project};
